For solving VPGs we distinguish two general approaches, the first approach is to simply project the VPG to the different configurations and solve all the resulting parity games independently. We call this \textit{independently} solving a VPG. Alternatively we solve the VPG \textit{collectively}, where a VPG is solved in its entirety and similarities between the configurations are used to improve performance. 

In the next sections we explore collective algorithms and analyse their time complexity. We aim to solve VPGs originating from model verification problems, such VPGs generally have certain properties that a completely random VPG might not have. In general parity games originating from model verification problems have a relatively low number of distinct priorities compared to the number of vertices because new priorities are only introduced when fixed points are nested in the $\mu$-calculus formula. Furthermore the transition guards of featured transition systems are expressed over features. In general these transition guards will be quite simple, specifically excluding or including a small number of features.

\subsection{Global vs local solving}
Parity games can be solved \textit{globally} or \textit{locally}; globally solving a parity game means that for every vertex in the game it is determined who the winner is. Locally solving a parity game means that for a specific vertex in the game it is determined who the winner is. For some applications of parity games, including model checking, there is a specific vertex that needs to be solved to solve the model checking problem so locally solving the parity game is sufficient for solving the original problem.

Similarly VPGs can be solved globally or locally where locally solving a VPG means determining for which configurations a certain vertex is won by player $0$ and for which configurations the vertex is won by player $1$.

Most parity game algorithms are concerned with global solving, when talking about solving a (V)PG we talk about globally solving it unless noted otherwise. For VPGs we consider a global and a local variant for every collective algorithm we are going to consider. When solving a VPG globally we might encounter significant differences in parts of the game or intermediate results between configurations that we don't encounter when solving it locally because we can terminate earlier. Therefore we hypothesize that the increase in performance between globally-collectively solving VPGs and locally-collectively solving VPGs is greater than the increase performance between globally-independently solving VPGs and locally-independently solving VPGs.