\documentclass[]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{tikz}
\usetikzlibrary{matrix}

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}



%opening
\title{Verifying Featured Transition Systems using Variability Parity Games}
\author{Sjef van Loo}

\begin{document}

\maketitle

\section{Introduction}
\input{introduction}

\section{Definitions}
\subsection{Transition systems}
Similar to \cite{Classen2013FeaturedTS}.

\begin{definition}
	\label{def_lts}An LTS is a tuple $M = (S, Act, trans, s_0)$, where:
	\begin{itemize}
		\item $S$ is a set of states,
		\item $Act$ a set of actions,
		\item $trans \subseteq S \times Act \times S$ is the transition relation with $(s,a,s') \in trans$ denoted by $s \xrightarrow a s'$,
		\item $s_0 \in S$ is the initial state.
	\end{itemize}
\end{definition}

\begin{definition}
	\label{def_fts}An FTS is a tuple $M = (S, Act, trans, s_0, N, P, \gamma)$, where:
	\begin{itemize}
		\item $S, Act, trans, s_0$ are defined as in an LTS,
		\item $N$ is a non-empty set of features,
		\item $P \subseteq \mathcal{P}(N)$ is a set of products, ie. feature assignments, that are valid,
		\item $\gamma : trans \rightarrow \mathbb{B}(N)$ is a total function, labelling each transition with a Boolean expression over the features. A product $p \in \mathcal{P}(N)$ satisfying the Boolean expression of transition $t$ is denoted by $p \models \gamma(t)$, $\gamma(t)(p) = 1$ or $p \in [\![\gamma(t)]\!]$. 
		
		A transition $s \xrightarrow a s'$ and $\gamma((s,a,s')) = f$ is denoted by $s \xrightarrow {a / f} s'$. 
	\end{itemize}
\end{definition}

\begin{definition}
	\label{def_fts_proj}
	The projection of an FTS $M$ to a product $p \in P$, noted $M_{|p}$, is the LTS $M'=(S,Act,trans', s_0)$, where $trans' = \{t \in trans\ |\ p \models \gamma(t)\}$.
\end{definition}

\begin{definition}
	\label{def_mu_syntax}\cite{Groote}
	A modal $\mu$-calculus formula over the set of actions $Act$ and a set of variables $\mathcal{X}$ is defined by
	\[ \varphi = \top\ |\ \bot\ |\ X\ |\ \varphi \vee \varphi\ |\ \varphi \wedge \varphi\ |\ \langle a \rangle \varphi\ |\ [a]\varphi\ |\ \mu X.\varphi\ |\ \nu X.\varphi \]
	with $a \in Act$ and $X \in \mathcal{X}$. 
	
	
	No negations in the language because negations can be pushed inside to the propositions, ie. the $\top$ and $\bot$ elements.
\end{definition}
A fixed point formula $ \sigma X. \varphi$, with $\sigma \in \{\mu,\nu\}$, can be unfolded which results in the formula $\varphi$ where very $X$ is replaced by $\sigma X. \varphi$, ie. $\varphi[X:=\sigma X. \varphi]$. A fixed point formula is equivalent to its unfolding, ie. $\sigma X. \varphi$ is equivalent to $\varphi[X:=\sigma X. \varphi]$. \cite{Bradfield2018}

\begin{definition} 
	\label{def_mu_sem}\cite{Groote} For LTS $(S, Act, trans, s_0)$ we inductively define the interpretation of a modal $\mu$-calculus formula $\varphi$, notation
	$[\![ \varphi ]\!]^\rho$, where $\rho : \mathcal{X} \rightarrow \mathcal{P}(S)$ is a logical variable valuation, as a set of states
	where $\varphi$ is valid, by:
	\begin{align*}
	&[\![ \mathit{\top} ]\!]^\rho &&= S\\
	&[\![ \mathit{\bot} ]\!]^\rho &&= \emptyset\\
	&[\![ \varphi_1 \wedge \varphi_2 ]\!]^\rho &&= [\![ \varphi_1 ]\!]^\rho \cap [\![ \varphi_2 ]\!]^\rho \\
	&[\![ \varphi_1 \vee \varphi_2 ]\!]^\rho &&= [\![ \varphi_1 ]\!]^\rho \cup [\![ \varphi_2 ]\!]^\rho\\
	&[\![ \langle a \rangle \varphi ]\!]^\rho &&= \{s \in S|\exists_{s' \in S} s \xrightarrow {a} s' \wedge s' \in [\![ \varphi ]\!]^\rho\}\\
	&[\![ [ a ] \varphi ]\!]^\rho &&= \{s \in S|\forall_{s' \in S} s \xrightarrow {a} s' \implies s' \in [\![ \varphi ]\!]^\rho\}\\
	&[\![ \mu X. \varphi ]\!]^\rho &&= \bigcap_{f \subseteq S}\{f | f = [\![ \varphi ]\!]^{\rho[X:=f]}\}\\
	&[\![ \nu X. \varphi ]\!]^\rho &&= \bigcup_{f \subseteq S}\{f | f = [\![ \varphi ]\!]^{\rho[X:=f]}\}\\
	&[\![ X ]\!]^\rho &&= \rho(X)
	\end{align*}
\end{definition}
\begin{definition}
	\label{def_sat}
	Given LTS $M = (S, Act, trans, s_0)$, state $s \in S$ and mu-calculus formula $\varphi$ we write $M,s \models \varphi$ if and only if $\varphi$ is satisfied in state $s$ for LTS $M$. If $M, s_0 \models \varphi$ we write $M \models \varphi$.
\end{definition}
\section{Goal}
Similar to \cite{inproceedings}.

Given an FTS $M = (S, Act, trans, s_0, N, P, \gamma)$ and a modal $\mu$-calculus formula $\varphi$ we want to find the set $P_s \subseteq P$ such that:
\begin{itemize}
	\item for every $p \in P_s$ we have $M_{|p} \models \varphi$,
	\item for every $p \in P \backslash P_s$ we have $M_{|p} \not\models \varphi$.
\end{itemize}
A counterexample for every $p \in P \backslash P_s$ is preferred.

If $P_s = P$, ie. all products satisfy $\varphi$, we write $M \models \varphi$.

\section{Parity Games}
\subsection{Parity games}
\begin{definition}
	\label{def_PG}\cite{Bradfield2018}
	A parity game (PG) is a tuple $(V, V_0, V_1, E, \rho)$, where:
	\begin{itemize}
		\item $V = V_0 \cup V_1$ and $V_0 \cap V_1 = \emptyset$,
		\item $V_0$ is the set of vertices owned by player $0$,
		\item $V_1$ is the set of vertices owned by player $1$, 
		\item $E \subseteq V \times V$ is the edge relation,
		\item $\rho :  V \rightarrow \mathbb{N}$ is a priority assignment.
	\end{itemize}
\end{definition}
We write $\alpha \in \{0,1\}$ to denote an arbitrary player. We write $\overline{\alpha}$ to denote $\alpha$'s opponent, ie. $\overline{0} = 1$ and $\overline{1} = 0$.

A parity game is played by players 0 and 1. A play starts with placing a token on vertex $v \in V$. Player $\alpha$ moves the token if the token is on a vertex owned by $\alpha$, ie. $v \in V_\alpha$. The token can be moved to $w \in V$, with $(v,w) \in E$. A series of moves results in a sequence of vertices, called path. For path $\pi$ we write $\pi_i$ to denote the $i^{\text{th}}$ vertex in path $\pi$. A play ends when the token is on vertex $v \in V_\alpha$ and $\alpha$ can't move the token anywhere, in this case player $\overline{\alpha}$ wins the play. If the play results in an infinite path $\pi$ then we determine the highest priority that occurs infinitely often in this path, formally
\[ \max\{ p \ |\ \forall_j \exists_i j < i \wedge p = \rho(\pi_i) \}\] 
If the highest priority is odd then player $1$ wins, if it is even player $0$ wins.

A strategy for player $\alpha$ is a function $\sigma : V^*V_\alpha \rightarrow V$ that maps a path ending in a vertex owned by player $\alpha$ to the next vertex. Parity games are positionally determined \cite{Bradfield2018}, therefore a strategy $\sigma: V_\alpha \rightarrow V$ that maps the current vertex to the next vertex is sufficient. 

A strategy $\sigma$ for player $\alpha$ is winning from vertex $v$ if and only if any play that results from following $\sigma$ results in a win for player $\alpha$. The graph can be divided in two partitions $W_0 \subseteq V$ and $W_1 \subseteq V$, called winning sets. If and only if $v \in W_\alpha$ then player $\alpha$ has a winnings strategy from $v$. Every vertex in the graph is either in $W_0$ or $W_1$ \cite{Bradfield2018}. Furthermore finite parity games are decidable \cite{Bradfield2018}.
\subsection{Featured parity games}
\begin{definition}
	\label{def_FPG}
	A featured parity game (FPG) is a tuple $(V,V_0, V_1, E, \rho, N, P, \gamma)$, where:
	\begin{itemize}
		\item $V = V_0 \cup V_1$ and $V_0 \cap V_1 = \emptyset$,
		\item $V_0$ is the set of vertices owned by player $0$,
		\item $V_1$ is the set of vertices owned by player $1$, 
		\item $E \subseteq V \times V$ is the edge relation,
		\item $\rho :  V \rightarrow \mathbb{N}$ is a priority assignment,
		\item $N$ is a set of features,
		\item $P \subseteq \mathcal{P}(N)$ is a set of products, ie. feature assignments, for which the game can be played,
		\item $\gamma : E \rightarrow \mathbb{B}(N)$ is a total function, labelling each edge with a Boolean expression over the features.
	\end{itemize}
\end{definition}
An FPG is played similarly to a PG, however the game is played for a specific product $p \in P$. Player $\alpha$ can only move the token from $v \in V_\alpha$ to $w \in V$ if $(v,w) \in E$ and $p \models \gamma(v,w)$.

A game played for product $p \in P$ results in winnings sets $W_0^p$ and $W_1^p$, which are defined similar to the $W_0$ and $W_1$ winning sets for parity games.

\begin{definition}
	\label{def_FPG_proj}
The projection from FPG $G = (V,V_0, V_1, E, \rho, N, P, \gamma)$ to a product $p \in P$, noted $G_{|p}$, is the parity game $(V,V_0,V_1, E', \rho)$ where $E' = \{ e \in E\ |\ p \models \gamma(e) \}$.
\end{definition}

Playing FPG $G$ for a specific product $p\in P$ is the same as playing the PG $G_{|p}$. Any path that is valid in $G$ for $p$ is also valid in $G_{|p}$ and vice versa. Therefore the strategies are also interchangeable, furthermore the winning sets $W_\alpha$ for $G_{|p}$ and $W_\alpha^p$ for $G$ are identical. Since parity games are positionally determined so are FPGs. Similarly, since finite parity games are decidable, so are finite FPGs.

\subsection{Variability parity games}
\begin{definition}
	\label{def_VPG}
	A variability parity game (VPG) is a tuple $(V,V_0, V_1, E, \rho, \mathfrak{C}, \theta)$, where:
	\begin{itemize}
		\item $V = V_0 \cup V_1$ and $V_0 \cap V_1 = \emptyset$,
		\item $V_0$ is the set of vertices owned by player $0$,
		\item $V_1$ is the set of vertices owned by player $1$, 
		\item $E \subseteq V \times V$ is the edge relation; we assume that $E$ is total, i.e. for all $v\in V$ there is some $w \in V$ such that $(v,w) \in E$,
		\item $\rho :  V \rightarrow \mathbb{N}$ is a priority assignment,
		\item $\mathfrak{C}$ is a finite set of configurations,
		\item $\theta : E \rightarrow \mathcal{P}(\mathfrak{C})\ \backslash\ \{0\}$ is the configuration mapping, satisfying for all $v \in V$, $\bigcup\{\theta(v,w)|(v,w) \in E\} = \mathfrak{C}$.
	\end{itemize}
\end{definition}
A VPG is played similarly to a PG, however the game is played for a specific configuration $c \in \mathfrak{C}$. Player $\alpha$ can only move the token from $v \in V_\alpha$ to $w \in V$ if $(v,w) \in E$ and $c \in \theta(v,w)$. Furthermore VPGs don't have deadlocks, every play results in an infinite path.

A game played for configuration $c \in \mathfrak{C}$ results in winning sets $W_0^c$ and $W_1^c$, which are defined similar to the $W_0$ and $W_1$ winning sets for parity games.

\begin{definition}
	\label{def_VPG_proj} The projection from VPG $G = (V, V_0, V_1, E, \rho, \mathfrak{C}, \theta)$ to a configuration $c \in \mathfrak{C}$, noted $G_{|c}$, is the parity game $(V, V_0, V_1, E', \rho)$ where $E' = \{ e\in E | c \in \theta(e)\}$.
\end{definition}

Playing VPG $G$ for a specific configuration $c \in \mathfrak{C}$ is the same as playing the PG $G_{|c}$. Any path that is valid in $G$ for $c$ is also valid in $G_{|c}$ and vice versa. Therefore the strategies are also interchangeable, furthermore the winning sets $W_\alpha$ for $G_{|c}$ and $W_\alpha^c$ for $G$ are identical. Since parity games are positionally determined so are VPGs. Similarly, since finite parity games are decidable, so are finite VPGs.

\subsection{Creating parity games}
Originating from an FTS and a modal $\mu$-calculus we can create an FPG (from which we can create a PG by projection) and from the FPG we can create a VPG. For a specific product we can project the FTS to an LTS, from which we can create a PG. The relation between the transition systems and games is displayed in the following diagram.
\\\begin{tikzpicture}
\matrix (m) [matrix of math nodes,row sep=4em,column sep=4em,minimum width=2em]
{
	\text{FTS} & \text{FPG} & \text{VPG} \\
	\text{LTS} & \text{PG} \\};
\path[-stealth]
(m-1-1) edge [double] node [left] {$\Pi$} (m-2-1)
edge node [above] {$\varphi$} (m-1-2)
(m-2-1.east|-m-2-2) edge node [above] {$\varphi$}
 (m-2-2)
(m-1-2) edge [double] node [right] {$\Pi$} (m-2-2)
edge (m-1-3);
\end{tikzpicture}\\
The projections are defined in the previous section. In this section we will define the horizontal arrows in the diagram. First we show how to create a PG from an LTS and a  modal $\mu$-calculus formula, this part is well studied and the approach is based on \cite{Bradfield2018}.


\begin{definition}
	\label{def_LTS2PG}\cite{Bradfield2018}
	LTS2PG($M, \varphi$) converts LTS $M = (S, Act, trans, s_0)$ and closed formula $\varphi$ to a PG $(V, V_0, V_1, E, \rho)$.
	
	A vertex in the parity game is represented by a pair $(s, \psi)$ where $s \in S$ and $\psi$ is a modal $\mu$-calculus formula. We will create a vertex for every state with every subformula of $\varphi$ except subformula's of the form $X$. Furthermore we create a vertex for every state with the unfolding of every fixpoint formula. Formally we define the set of vertices by first defining the set of subformula's:
	\[ F = \{ \psi\ |\ \psi \text{ is a subformula of } \varphi \} \text{, note that $\varphi$ is a subformula of $\varphi$} \]
	The set of subformula's that are of the form $X$:
	\[ F_X = \{ \psi \in F\ |\ \psi = X\} \]
	 And the set of the unfolding of fixedpoint subformula's:
	 \[ F_\sigma = \{\psi[X:=\sigma X. \psi]\ |\ \sigma X. \psi \in F \text{ with } \sigma \in \{\mu, \nu\}\} \]
	Having these sets we can define the set of vertices by:
	\[ V = S \times (F \backslash F_X \cup F_{\sigma})\]
	
	We create the parity game with the smallest set $E$ such that:
	\begin{itemize}
		\item $V = V_0 \cup V_1$,
		\item $V_0 \cap V_1 = \emptyset$ and
		\item for every $v = (s, \psi) \in V$ we have:
		\begin{itemize}
			\item If $\psi = \top$ then $v \in V_1$.
			\item If $\psi = \bot$ then $v \in V_0$.
			\item If $\psi = \psi_1 \vee \psi_2$ then:
				\subitem $v \in V_0$,
				\subitem $(v, (s,\psi_1)) \in E$ and
				\subitem $(v, (s,\psi_2)) \in E$.
			\item If $\psi = \psi_1 \wedge \psi_2$ then:
				\subitem $v \in V_1$,
				\subitem $(v, (s,\psi_1)) \in E$ and
				\subitem $(v, (s,\psi_2)) \in E$.
			\item If $\psi = \langle a \rangle \psi_1$ then $v \in V_0$ and for every $s \xrightarrow{ a} s'$ we have $(v, (s', \psi_1)) \in E$.
			\item If $\psi = [ a ] \psi_1$ then $v \in V_1$ and for every $s \xrightarrow{ a} s'$ we have  $(v, (s', \psi_1)) \in E$.
			\item If $\psi = \mu X. \psi_1$ then $(v, (s, \psi_1[X:=\mu X. \psi_1])) \in E$.
			\item If $\psi = \nu X. \psi_1$ then $(v, (s, \psi_1[X:=\nu X. \psi_1])) \in E$.
		\end{itemize}
	Note that since $\varphi$ is closed and we use unfolding there will never be an edge $(v,(s, X)) \in E$.
	\end{itemize}


Finally we have $\rho(s, \psi) = \begin{cases}
2 \lfloor adepth(X) / 2 \rfloor & \text{if } \psi = \nu X. \psi'\\
2 \lfloor adepth(X) / 2 \rfloor + 1 & \text{if } \psi = \mu X. \psi'\\
0 & \text{otherwise}
\end{cases}$
\end{definition}
Next we define the transformation from FTS to FPG.
\begin{definition}
	\label{def_FTS2FPG}
	FTS2FPG($M, \varphi$) converts FTS $M = (S, Act, trans, s_0, N, P, \gamma)$ and closed formula $\varphi$ to FPG $(V, V_0, V_1, E, \rho, N, P, \gamma')$.
	
	We have $(V, V_0, V_1, E, \rho)$ = LTS2PG($(S, Act, trans, s_0), \varphi$) and
	\[ \gamma'((s, \psi),(s', \psi')) = \begin{cases}
	\gamma(s,a,s') & \text{if }\psi = \langle a \rangle \psi'\text{ or }\psi = [a]\psi' \\
	\top & \text{otherwise}
	\end{cases}\]
\end{definition}
Finally we define how to create a VPG from an FPG. This transformation abstracts from the notion of products and uses configurations for a syntactically more pleasant representation. Furthermore in VPGs deadlocks are removed, this is done by creating two losing vertices $l_0$ and $l_1$ such that player $\alpha$ loses when the token is in vertex $l_\alpha$. Any vertex that can not move for a configuration will get an edge that is admissible for that configuration towards one of the losing vertices.
\begin{definition}
	\label{def_FPG2VPG}
	FPG2VPG($G^F$) converts FPG $G^F = (V^F, V_0^F, V_1^F, E^F, \rho^F, N, P, \gamma)$ to VPG $G = (V, V_0, V_1, E, \rho, \mathfrak{C}, \theta)$.
	
	Let $P$ be defined as  $\{p_0, p_1, \dots, p_m\}$, we define $\mathfrak{C} = \{c_0, c_1, \dots, c_m\}$.
	
	We create vertices $l_0$ and $l_1$ and define $V_0 = V_0^F \cup \{l_0\}$, $V_1 = V_1^F \cup \{l_1\}$ and $V = V_0 \cup V_1$.
	
	We construct $E$ by first making $E = E^F$ and adding edges $(l_0, l_0)$ and $(l_1, l_1)$ to $E$. Simultaneously we construct $\theta$ by first making $\theta(e) = \{c_i \in \mathfrak{C} | p_i \models \gamma(e)\}$ for every $e \in E^F$. Furthermore $\theta(l_0,l_0) = \theta(l_1,l_1) = \mathfrak{C}$.
	
	Next, for every vertex $v \in V_\alpha$ with $\alpha = \{0,1\}$, we have $C = \mathfrak{C} \backslash \bigcup \{\theta(v,w)|(v,w) \in E\}$. If $C \neq \emptyset$ then we add $(v, l_\alpha)$ to $E$ and make $\theta(v,l_\alpha) = C$.
	Finally we have 
	\[ \rho(v) = \begin{cases}
	1  & \text{if } v = l_0 \\
	0 & \text{if } v = l_1 \\
	\rho^F(v) &\text{otherwise}
	\end{cases} \]
\end{definition}

\subsection{Correctness}
\begin{theorem}
	\label{the_PGsubPGA} Given:
	\begin{itemize}
		\item FTS $M = (S,Act, trans, s_0, N, P, \gamma)$,
		\item a closed modal mu-calculus formula $\varphi$,
		\item a product $p \in P$
	\end{itemize}
	it holds that he parity games LTS2PG($M_{|p}, \varphi$) and FTS2FPG($M, \varphi$)$_{|p}$  are identical.
\begin{proof}
	Let $G^F = $FTS2FPG($M, \varphi$)$ = (V^F, V_0^F, V_1^F, E^F, \rho^F, N, P, \gamma')$, using definition \ref{def_FTS2FPG}, and $G^F_{|p} = (V^F, V_0^F, V_1^F, {E^F}', \rho^F)$, using definition \ref{def_FPG_proj}. Furthermore we have $M_{|p} = (S, Act, trans', s_0)$ and we let $G = $ LTS2PG$(M_{|p}, \varphi) = (V, V_0, V_1, E, \rho)$. We depict the different transition systems and games in the following diagram.
	
	\begin{tikzpicture}
	\matrix (m) [matrix of math nodes,row sep=4em,column sep=1em,minimum width=2em]
	{
		\text{\ \ FTS }M & \  &\ & \text{FPG } G^F  \\
		\text{LTS }M_{|p} & \ & \text{PG } G & \text{\ \ PG }G_{|p}^F \\};
	\path[-stealth]
	(m-1-1) edge [double] node [left] {$\Pi$} (m-2-1)
	edge node [above] {$\varphi$} (m-1-4)
	(m-2-1.east|-m-2-3) edge node [above] {$\varphi$}
	(m-2-3)
	(m-1-4) edge [double] node [right] {$\Pi$} (m-2-4);
	\end{tikzpicture}\\
	We will prove that $G = G_{|p}^F$. We first note that game $G$ is created by 
	\[  (V, V_0, V_1, E, \rho) = LTS2PG((S, Act, trans', s_0),\varphi) \]
	and the vertices, edges and priorities of game $G^F$ are created by 
	\[ (V^F, V_0^F, V_1^F, E^F, \rho^F) = LTS2PG((S,Act, trans, s_0), \varphi)\]
	Using the definition of LTS2PG (\ref{def_LTS2PG}) we find that the vertices and the priorities only depend on the states in $S$ and the formula $\varphi$, since these are identical in the above two statements we immediately get $V = V^F, V_0 = V_0^F, V_1 = V_1^F$ and $\rho = \rho^F$. The vertices and priorities don't change when an FTS is projected, therefore $G_{|p}^F$ has the same vertices and priorities as $G^F$.
	
	Now we are left with showing that $E = {E^F}'$ in order to conclude that that $G = G^F_{|p}$. We will do this by showing $E \subseteq {E^F}'$ and $E \supseteq {E^F}'$.
	
	First let $e \in E$. Note that a vertex in the parity game is represented by a pair of a state and a formula. So we can write $e = ((s,\psi),(s',\psi'))$. To show that $e \in {E^F}'$ we distinguish two cases:
	\begin{itemize}
		\item  If $\psi = \langle a \rangle \psi_1$ or $\psi = [a] \psi_1$ then there exists an $a \in Act$ such that $(s,a,s') \in trans'$. Using definition \ref{def_fts_proj} we get $(s,a,s') \in trans$ and $p \models \gamma(s,a,s')$. Using definition \ref{def_FTS2FPG} we find that $\gamma'((s,\psi),(s',\psi')) = \gamma(s,a,s')$ and therefore $p \models \gamma'((s,\psi),(s',\psi'))$. Now using definition \ref{def_FPG_proj} we find $((s,\psi),(s',\psi')) \in {E^F}'$.
		\item Otherwise the existence of the edge does not depend on the $trans$ parameter and therefore $((s,\psi),(s',\psi')) \in {E^F}'$ if $(s,\psi) \in V^F$, since $V^F = V$ we have $(s,\psi) \in V^F$.
	\end{itemize}
	We can conclude that $E \subseteq {E^F}'$, next we will show $E \supseteq {E^F}'$. Let $e = ((s,\psi),(s',\psi')) \in {E^F}'$. We distinguish two cases:
	\begin{itemize}
		\item If $\psi = \langle a \rangle \psi_1$ or $\psi = [a] \psi_1$ then there exists an $a \in Act$ such that $(s,a,s') \in trans$. Using definition \ref{def_FPG_proj} we get $p \models \gamma'(s,a,s')$. Using definition \ref{def_FTS2FPG} we get $p \models \gamma(s,a,s')$. Using the projection definition \ref{def_FTS2FPG} we get $(s,a,s') \in trans'$ and therefore $((s,\psi),(s',\psi'))\in E$.
		\item Otherwise the existence of the edge does not depend on the $trans$ parameter and therefore $((s,\psi),(s',\psi')) \in E$ if $(s,\psi) \in V$, since $V^F = V$ we have $(s,\psi) \in V$.
	\end{itemize}
	\end{proof}
\end{theorem}

\begin{theorem}
	\label{the_FPG_ver_FTS}
	Given:
	\begin{itemize}
		\item FTS $M = (S, Act, trans, s_0, N, P, \gamma)$,
		\item closed modal mu-calculus formula $\varphi$,
		\item product $p \in P$ and
		\item state $s \in S$
	\end{itemize}
it holds that $M_{|p}, s \models \varphi$ if and only if $(s, \varphi) \in W_0^p$ in FTS2FPG($M, \varphi$).
\begin{proof}
	The winning set $W_\alpha^p$ is equal to winning set $W_\alpha$ in FTS2FPG($M, \varphi$)$_{|p}$ using definition \ref{def_FPG}. Using theorem \ref{the_PGsubPGA} we find that the game FTS2FPG($M, \varphi$)$_{|p}$ is equal to the game LTS2PG($M_{|p}, \varphi$), obviously their winning sets are also equal. Using the modal verification proof from \cite{Bradfield2018} we know that $M_{|p}, s \models \varphi$ if and only if $(s, \varphi) \in W_0$. Winning set $W_\alpha^p$ is equal to $W_\alpha$, therefore the theorem holds.
\end{proof}
\end{theorem}

\begin{theorem}
	\label{the_FPG_sub_VPG}
	Given:
	\begin{itemize}
		\item FPG $G^F = (V^F, V_0^F, V_1^F, E^F, \rho^F, N, \{p_0, p_1, \dots, p_m\}, \gamma)$,
		\item product $p_i$,
		\item player $\alpha \in \{0,1\}$
	\end{itemize}
we have for winning sets $W_\alpha^{p_i}$ in $G$ and $W_\alpha^{c_i}$ in FPG2VPG($G^F$) that $W_\alpha^{p_i} \subseteq W_\alpha^{c_i}$.
\begin{proof}
	Let $G = (V,V_0,V_1, E, \rho, \mathfrak{C},\theta) =$ FPG2VPG($G^F$). Consider finite play $\pi$ that is valid in game $G^F$ for product $p_i$. We have for every $(\pi_i, \pi_{i+1})$ in $\pi$ that $(\pi_i, \pi_{i+1}) \in E^F$ and $p_i \models \gamma((\pi_i, \pi_{i+1}))$. From definition \ref{def_FPG2VPG} it follows that $(\pi_i, \pi_{i+1}) \in E$ and $c_i \in \theta(\pi_i, \pi_{i+1})$. So we can conclude that path $\pi$ is also valid in game $G$ for configuration $c_i$. Since the play is finite the winner is determined by the last vertex $v$ in $\pi$, player $\alpha$ wins such that $v \in V_{\overline{\alpha}}$. Furthermore we know, because the play is finite, that there exists no $(v,w) \in E^F$ with $p \models \gamma(v,w)$. From this we can conclude that $(v, l_{\overline{\alpha}}) \in E$ and $c_i \in \theta(v, l_{\overline{\alpha}})$. Vertex $l_{\overline{\alpha}}$ has one outgoing edge, namely to itself. So finite play $\pi$ will in game $G^F$ results in an infinite play $\pi(l_{\overline{\alpha}})^\omega$. Vertex $l_{\overline{\alpha}}$ has a priority with the same parity as player $\alpha$, so player $\alpha$ wins the infinite play in $G$ for configuration $c_i$.
	
	Consider infinite play $\pi$ that is valid in game $G^F$ for product $p_i$. As shown above this play is also valid in game $G$ for configuration $c_i$. Since the win conditions of both games are the same the play will result in the same winner.
	
	Consider infinite play $\pi$ that is valid in game $G$ for configuration $c_i$. We distinguish two cases:
	\begin{itemize}
		\item If $l_\alpha$ doesn't occur in $\pi$ then the path is also valid for game $G^F$ with product $p_i$ and has the same winner.
		\item If $\pi = \pi'(l_\alpha)^\omega$ then the winner is player $\overline{\alpha}$. The path $\pi'$ is valid for game $G^F$ with product $p_i$. Let vertex $v$ be the last vertex of $\pi'$. Since $(v, l_\alpha) \in E$ and $c_i \in \theta(v,l_\alpha)$ we know that there is no $(v,w) \in E^F$ with $p_i \models \gamma(v,w)$ and that vertex $v$ is owned by player $\alpha$. So in game $G^F$ player $\alpha$ can't move at vertex $v$ and therefore loses the game (in which case the winner is also $\overline{\alpha}$.
	\end{itemize}

We have shown that every path (finite or infinite) in game $G^F$ with product $p_i$ can be played in game $G$ with configuration $c_i$ and that they have the same winner. Furthermore every infinite path in game $G$ with configuration $c_i$ can be either played as an infinite path or the first part of the path can be played in $G^F$ with product $p_i$ and they have the same winner. From this we can conclude that the theorem holds.
\end{proof}
\end{theorem}
\bibliography{mybib} 
\bibliographystyle{ieeetr}

\end{document}
