We can consider a VPG as a PG that is the union of all its projections. We call the resulting PG the \textit{unification} of the VPG.
\begin{definition}
Given VPG $\hat{G} = (\hat{V},\hat{V}_0,\hat{V}_1, \hat{E},\hat{\Omega}, \mathfrak{C},\theta)$ we define the unification of $\hat{G}$, denoted as $\hat{G}_{\downarrow}$, as
\[  \hat{G}_{\downarrow} = \bigcup_{c\in \mathfrak{C}}\hat{G}_{|c} \]
where the union of two PGs is trivially defined as
\[ (V,V_0,V_1,E,\Omega) \cup (V',V_0',V_1',E',\Omega') = (V \uplus V', V_0 \uplus V_0', V_1 \uplus V_1', E \uplus E', \Omega \uplus \Omega') \]
\end{definition}
We will use the hat decoration ($\hat{G},\hat{V},\hat{E},\hat{\Omega},\hat{W}$) when referring to a VPG and use no hat decoration when referring to a PG.

Every vertex in game $\hat{G}_{\downarrow}$ originates from a configuration and an original vertex. Therefore we can consider every vertex in a unification as a pair consisting of a vertex and a configuration, ie. $V = \mathfrak{C} \times \hat{V}$. We can consider edges in a unification similarly, ie. $E \subseteq (\mathfrak{C} \times \hat{V}) \times (\mathfrak{C} \times \hat{V})$. Note that edges don't cross configurations, ie. for every $((c,\hat{v}) , (c',\hat{v}')) \in E$ we have $c = c'$.

If we solve the PG that is the unification of a VPG we have solved the VPG, as shown in the next theorem .
\begin{theorem}
	\label{theA_solve_UVPG_is_solve_VPG}
	Given VPG $\hat{G} =  (\hat{V},\hat{V}_0,\hat{V}_1, \hat{E},\hat{\Omega}, \mathfrak{C},\theta)$. For winning sets $W_0$ and $W_1$ for game $\hat{G}_{\downarrow}$ and winning sets $\hat{W}^c_0$ and $\hat{W}^c_1$ for some configuration $c \in \mathfrak{C}$ it holds that
	\[(c,\hat{v}) \in W_\alpha \iff \hat{v} \in \hat{W}^c_\alpha  \text{, for }\alpha \in \{0,1\}  \]
	\begin{proof}
		The bi-implication is equal to  the following to implications.
		\[ (c,\hat{v}) \in W_\alpha \implies \hat{v} \in \hat{W}^c_\alpha  \text{, for }\alpha \in \{0,1\} \]
		and
		\[ (c,\hat{v}) \notin W_\alpha\implies \hat{v} \notin \hat{W}^c_\alpha \text{, for }\alpha \in \{0,1\}  \]
		
		Since the winning sets partition the game we have $\hat{v} \notin \hat{W}^c_\alpha \implies \hat{v} \in \hat{W}^c_{\overline{\alpha}}$ (similar for set $W$). Therefore it is sufficient to prove the first implication.
		
		Let $(c,\hat{v}) \in W_\alpha$, player $\alpha$ has a strategy to win game $\hat{G}_{\downarrow}$ from vertex $(c,\hat{v})$. Since $\hat{G}_{\downarrow}$ is the union of all the projections of $\hat{G}$ we can apply the same strategy to game $\hat{G}_{|c}$ to win vertex $\hat{v}$ as player $\alpha$. Because we can win $\hat{v}$ in the projection of $\hat{G}$ to $c$ we have $\hat{v} \in \hat{W}^c_\alpha$.
	\end{proof}
\end{theorem}

One of the properties of a PG is its totality; a game is total if every vertex has at least 1 outgoing vertex. Plays in a total PG will always result in an infinite path. VPGs are total, meaning that every vertex has, for every configuration $c \in \mathfrak{C}$ at least 1 outgoing vertex admitting $c$. Because VPGs are total a unified VPG is also total. For unified VPGs we can however further investigate its totality by introducing the notion of being total for every configuration. 
\begin{definition}
	A unified VPG $(V,V_0,V_1,E,\Omega)$ is total for every configuration iff for every $(c,v) \in V$ there exists a $(c,v') \in V$ such that $((c,v),(c,v')) \in E$.
\end{definition}

It follows that if a unified VPG is total then it is also total for every configuration as shown in the following lemma.
\begin{lemma}
	\label{lem_UVPG_total}
	A unified VPG $G = (V,V_0,V_1,E,\Omega)$ that is total is also total for every configuration.
	\begin{proof}
		Since $G$ is total we have for every $(c,v) \in V$ that there exists a $(c',v') \in V$ such that $((c,v),(c',v')) \in E$. Because unified VPGs don't have edges cross configurations we find that $c = c'$ and therefore $G$ is total for every configuration.
	\end{proof}
\end{lemma}


\subsubsection{Representing unified variability parity games}
Unified VPGs have a specific structure because they are the union of parity games that have the same vertices with the same owner and priority. Because they have the same priority we don't actually need to create a new function that is the unification of all the projections, we can simply use the original priority assignment function because the following relation holds:
\[ \hat{\Omega}(c,\hat{v}) = \Omega(\hat{v}) \]
Similarly we can use the original partition sets $\hat{V}_0$ and $\hat{V}_1$ instead of having the new partition $V_0$ and $V_1$ because the following relations holds:
\[ (c,\hat{v}) \in V_0 \iff \hat{v}\in \hat{V}_0 \]
\[ (c,\hat{v}) \in V_1 \iff \hat{v}\in \hat{V}_1 \]

So instead of considering unified VPG $(V,V_0,V_1,E,\Omega)$ we will consider $(V,\hat{V}_0,\hat{V}_1,E,\hat{\Omega})$. 

Using this definition we can easily project a unified VPG back to one of the parity games.
\begin{definition}
	The projection of unified VPG $G = (V,\hat{V}_0, \hat{V}_1,E,\hat{\Omega})$ to configuration $c$, denoted as $G_{|c}$, is the parity game $(V',\hat{V}_0,\hat{V}_1,E',\hat{\Omega})$ such that $V' = \{ \hat{v}\ |\ (c,\hat{v}) \in V \}$ and $E' = E \cap (V' \times V')$.
\end{definition}

Next we consider how we represent vertices and edges in a unified VPG. A set $X \subseteq (\mathfrak{C} \times \hat{V})$ can be represented as a complete function $f : \hat{V} \rightarrow 2^\mathfrak{C}$. The set $X$ and function $f$ are equivalent, denoted by the operator $=_\lambda$, iff the following relation holds:
\[ (c,\hat{v}) \in X \iff c \in f(\hat{v}) \]
We can also represent edges as a complete function $f : \hat{E} \rightarrow 2^\mathfrak{C}$. The set $E$ and function $f$ are equivalent, denoted by the operator $=_\lambda$, iff the following relation holds:
\[ ((c,\hat{v}),(c,\hat{v}')) \in E \iff c \in f(\hat{v},\hat{v}') \]
We write $\lambda^\emptyset$ to denote the function that maps every element to $\emptyset$, clearly $\lambda^\emptyset =_\lambda \emptyset$. We call using a set of pairs to represent vertices a \textit{set-wise} representation and using functions to represent vertices a \textit{function-wise} representation.